% 参考文献

\begin{thebibliography}{99}			% 参考文献数が二桁の場合
%\begin{thebibliography}{9}				% 参考文献数が一桁の場合


	\bibitem{bib:01}				% 英文論文の1
		Yang Lu,
		Industry 4.0: A survey on technologies, applications and open research issues,
		{\it  Industrial Information Integration}, 6, pp. ~1--10, 2017.

	\bibitem{bib:02}				% 英文論文の2
		Abir Gallala, Atal Anil Kumar, Bassem Hichri and Peter Plapper,
		Digital Twin for human–robot interactions by means of Industry 4.0 Enabling Technologies,
		{\it  Sensors}, ~23--13, pp. ~4950--4967, 2022.

	\bibitem{bib:03}				% 英文論文の3
		Zhao, Wenshuai, Jorge Peña Queralta, and Tomi Westerlund,
		Sim-to-real transfer in deep reinforcement learning for robotics: a survey,
		{\it  in Proceedings, 2020 IEEE symposium series on computational intelligence (SSCI)}, pp. ~737--744, 2020.

	\bibitem{bib:04}				% 英文論文の4
		Bilberg, Arne, and Ali Ahmad Malik,
		Digital twin driven human–robot collaborative assembly,
		{\it  CIRP annals}, ~68--1, pp. ~499--502, 2019.

	\bibitem{bib:05}				% 英文論文の5
		Grayce N. Schroeder, Charles Steinmetz, Carlos E. Pereira,
		Digital twin data modeling with automationml and a communication methodology for data exchange,
		{\it  IFAC-PapersOnLine}, ~49--30, pp. ~12--17, 2016.

	\bibitem{bib:06}				% 英文論文の6
		Vladimir Kutsa, Gianfranco E. Modonib, Tauno Ottoa, Marco Saccoc, Toivo Tähemaaa, Yevhen Bondarenkoa, and Ruxin Wanga,
		Synchronizing physical factory and its digital twin through an IIoT middleware: a case study,
		{\it  in Proceedings, the Estonian Academy of Sciences}, ~68--4, pp. ~364--370, 2019.

	\bibitem{bib:07}				% 英文論文の7
		C. J. Liang, W. McGee, C. C. Menassa, and V. R. Kamat,
		Bi-directional communication bridge for state synchronization between digital twin simulations and physical construction robots,
		{\it   in Proceedings, the International Symposium on Automation and Robotics in Construction (IAARC)}, pp. ~1480--1487, 2020, Kitakyushu, Japan.

	\bibitem{bib:08}				% 英文論文の8
		Xi Wang, Ci-Jyun Liang, Carol Menassa and Vineet Kamat,
		Real-Time Process-Level Digital Twin for Collaborative Human-Robot Construction Work,
		{\it  in Proceedings, the International Symposium on Automation and Robotics in Construction (IAARC)},  pp. ~1528--1535, 2020, Kitakyushu, Japan.

	\bibitem{bib:09}				% 英文論文の9
		Liang Du, Shugen Ma, Erina Tsuchiya and Mana Fuchimi,
		Paper-Made Grippers for Soft Food Grasping,
		{\it  in Proceedings, 17th International Conference on Ubiquitous Robots},  pp. ~362--367, 2020, Kyoto, Japan.
	% 具体例
	\bibitem{bib:10} 川崎 晴久：
		ロボット工学の基礎．
			森北出版，2020.

\end{thebibliography}
